\documentclass[12pt, letterpaper]{article}
\usepackage[margin=2cm]{geometry}
\pagestyle{plain}

\usepackage{amsmath, amsfonts, amssymb, amsthm}
\usepackage[shortlabels]{enumitem}
\usepackage{mathptmx}
\usepackage[makeroom]{cancel}
\usepackage{enumitem}


\allowdisplaybreaks


\begin{document}
\begin{center}
  {\section*{\normalfont\normalsize\bf Hearing Format}}
\end{center}

\vspace{12pt}

\noindent The Commissioner's hearing on the pipeline expansion proposal will
begin on Friday January $7^{th}$ at 9:00 AM MST and will conclude (at the latest) at
4:30 PM, MST.

\vspace{12pt}

\section*{\normalfont\normalsize\bf Time Allotment}
\noindent Time allocations are strict. Groups will be allotted 10 minutes to
present their arguments before the Commissioner group with an additional 5
minutes provided afterward for other groups to ask questions. An additional five
minutes following question periods are allotted to ensure a smooth transition
between presenting groups. Note that all times in the time table below indicate
start times.

\section*{\normalfont\normalsize\bf Setting}
\noindent The hearing will take place online through the social platform ZOOM. A
link will be provided in advance by way of email no later than Thursday at 5:00
pm.

\section*{\normalfont\normalsize\bf Hearing Ettiquette}
\noindent For the hearing to operate smoothly all individuals will be required
to follow a set of social etiquettes, so disturbances do not erupt:
\begin{enumerate}[label={\bf\arabic*}.]
  \item As per the course syllabus, dialogue within and between groups must be
    kept respectful at all times.
    Dr. Voth will be present to address transgressions of course policy as he
    sees fit.
  \item All participants who are not a part of the presenting group or have not
    been given the permission to speak must keep their microphone (mic) on mute.
  \item All participants are encouraged to turn on their camera while speaking,
    either during their presentation or when asking questions to foster a
    collaborative environment.
  \item Procedure must be followed in order to ask for clarification,  ask
    questions, or raise concerns:
    \begin{enumerate}[label={\bf\alph*}.]
      \item If you would like to ask a question during a question period, please use
        Zoom’s ‘raise hand’ function. Commissioners will review how to find this in
        the opening remarks.
      \item Commissioners will call on an individual with a raised hand to turn on
        their mic and ask their question. Individuals will be called on a
        first-come first-serve basis.
      \item Groups are encouraged to ask only one question at a time to give
        others an opportunity to participate. If there are no other questions and
        time permitting, we will offer the opportunity to ask additional questions.
    \end{enumerate}
  \item  The chat box will not be available throughout the hearing to avoid
    disruptions. If you have any questions for stakeholder groups, please
    reserve them for noted questions periods. If you have any questions for the
    Commissioners, please email Courtney ({\bf courtney.leblanc@ucalgary.ca}), this
    inbox will be actively monitored throughout the hearing.
\end{enumerate}

\newpage

\begin{center}
  {\section*{\normalfont\normalsize\bf Schedule}}
\end{center}

\vspace{12pt}

{\bf 9:00 AM - Commissioner opening remarks}

\vspace{12pt}

\hphantom{~~~~} 9:15 AM - Trekergy

\vspace{12pt}

\hphantom{~~~~} 9:35 AM - Sunchild First Nation

\vspace{12pt}

{\bf 5-minute bio break}

\vspace{12pt}

\hphantom{~~~~} 10:00 AM - United Conservative Party, Government of Alberta

\vspace{12pt}

\hphantom{~~~~} 10:20 AM - Alexander First Nation

\vspace{12pt}

\hphantom{~~~~} 10:40 AM - M\'{e}tis Nation British Columbia

\vspace{12pt}

{\bf 5-minute bio break}

\vspace{12pt}

\hphantom{~~~~} 11:05 AM - Alexis Sioux Nation

\vspace{12pt}

\hphantom{~~~~} 11:25 AM - New Democrat Party, Government of British Columbia

\vspace{12pt}

\hphantom{~~~~} 11:45 AM - Coldwater Indian Band

\vspace{12pt}

{\bf 1-hour lunch break; resume at 1:00 PM}

\vspace{12pt}

\hphantom{~~~~} 1:00 PM - Erminesken Cree Nation

\vspace{12pt}

\hphantom{~~~~} 1:20 PM - Musqueam First Nation

\vspace{12pt}

\hphantom{~~~~} 1:40 PM - City of Vancouver

\vspace{12pt}

{\bf 5-minute bio break}

\vspace{12pt}

\hphantom{~~~~} 2:05 PM - Squamish Nation

\vspace{12pt}

\hphantom{~~~~} 2:25 PM - Gunn Lake M\'{e}tis Local

\vspace{12pt}

\hphantom{~~~~} 2:45 PM - Tsleil-Waututh Nation

\vspace{12pt}

{\bf 10-minute bio break}

\vspace{12pt}

\hphantom{~~~~} 3:10 PM - 15-minute open queston period

\vspace{12pt}

\hphantom{~~~~} 3:25 PM - Trekergy closing considerations

\vspace{12pt}

\hphantom{~~~~} 3:30 PM - Statement of final positions from all attending parties

\vspace{12pt}

{\bf 3:45 PM - Commissioner closing remarks}

\vspace{12pt}

{\bf 3:50 PM - Dr. Voth's POLI345 closing remarks}
\end{document}
